Trends in the contribution of major causes of death to the black-white life expectancy gap

### 2017-05-21 conferences/ResearchDay/Riddell_ResearchDay_minimal.Rmd

---
title: "Long-term trends in the contribution of major causes of death to the black-white life expectancy gap by US state"
author: "Corinne Riddell, Post-doctoral Researcher, McGill University, Canada"
date: "May 23, 2017"
output: ioslides_presentation
---

@@

```{r, echo=F}
img1 <-  rasterGrob(as.raster(readPNG("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/k_morrison.png")), interpolate = FALSE)
img2 <-  rasterGrob(as.raster(readPNG("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/s_harper2.png")), interpolate = FALSE)
img3 <-  rasterGrob(as.raster(readJPEG("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/j_kaufman.jpg")), interpolate = FALSE)
grid.arrange(img3,
             img1,
             img2,
             ncol = 3)
```
Jay Kaufman, Supervisor        Kathryn Morrison, Post-doc       Sam Harper, Professor

@@

And also...

>- be broadly accessible,
>- be interactive,
>- be reproducible.

@@

+ Estimate smoothed mortality rates and impute coarsened data using a Bayesian time series model 
+ 1,000 posterior samples containing estimated *smoothed* and *imputed* death counts
+ For each sample:
    1. Create a life table for every strata
    2. Calculate the <b style = "greentext">difference</b> in life expectancy between blacks and whites
    3. Decompose the difference by age and cause of death
    4. Calculate age-standardized mortality rates
+ Calculate the mean, 5^th^ and 95^th^ percentiles for all estimates.
+ Compute national trend using random-effects meta regression

@@

##Tennessee
```{r, echo = F}
age_cod_results_female <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/age_cod_results_female.csv")

@@

##New York
```{r, echo = F}

@@

##Blah

-

>>>>

---
title: "Trends in the contribution of major causes of death to the black-white life expectancy gap"
author: "Corinne Riddell, Post-doctoral Researcher, McGill University, Canada"
date: "May 23, 2017"
output: ioslides_presentation
---

@@

```{r, echo=F}
img1 <-  rasterGrob(as.raster(readPNG("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/k_morrison.png")), interpolate = FALSE)
img2 <-  rasterGrob(as.raster(readPNG("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/s_harper2.png")), interpolate = FALSE)
img3 <-  rasterGrob(as.raster(readJPEG("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/conferences/ResearchDay/images/j_kaufman.jpg")), interpolate = FALSE)
grid.arrange(img3,
             img1,
             img2,
             ncol = 3)
```
Jay Kaufman, Kathryn Morrison, and Sam Harper

@@

@@

+ Estimated smoothed mortality rates using a Bayesian time series model with Poisson likelihood
+ Used a truncated Poisson likelihood when number of deaths were between 1 and 9
+ 1,000 posterior samples. For each:
    1. Create a life table for every strata
    2. Calculate the <b style = "greentext">difference</b> in life expectancy between blacks and whites
    3. Decompose the difference by age and cause of death
    4. Calculate age-standardized mortality rates
+ Calculate the mean, 5^th^ and 95^th^ percentiles for all estimates
+ Compute national trend using random-effects meta regression

@@

##Tennessee
```{r, echo = F, out.height = 600, out.width = 800}
age_cod_results_female <- read.csv("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/age_cod_results_female.csv")

@@

##New York
```{r, echo = F, out.height = 600, out.width = 800}

@@

##Learn more
- Working paper submitted to bioRxiv - will be public soon!
- Shiny app hosted online with our results here:  https://corinne-riddell.shinyapps.io/shiny_app/

**Get in touch**

- corinne.riddell@mail.mcgill.ca
- @datavisitor on Twitter
